Oracle

### 2018-08-28 2-newfiles.Rmd
update
polish SupMat

---
title: "New files"
author: "Florian Privé"
date: "20 octobre 2017"
output: html_document
---

@@

```{r}
snp_triple(celiac)
snp_triple(celiac2)
```

>>>>

---
title: "New files"
author: "Florian Privé"
date: "October 20, 2017"
output: html_document
---

@@

```{r}
celiac <- snp_attach("backingfiles/celiacQC.rds")
snp_triple(celiac)
snp_triple(celiac2)
```

### 2018-08-28 3-oracle.Rmd
polish SupMat

```{r, message=FALSE}
library(tidyverse)
library(bigsnpr)
library(foreach)
celiac2 <- snp_attach("backingfiles/celiacQC_sub1.rds")
CHR <- celiac2$map$chromosome
POS <- celiac2$map$physical.pos
(G <- celiac2$genotypes)
ind.HLA <- snp_indLRLDR(CHR, POS, subset(LD.wiki34, ID == "hild12"))
NCORES <- nb_cores()
```

```{r}
myggplot <- function(..., coeff = 1) {
  bigstatsr:::MY_THEME(ggplot(...), coeff = coeff)
} 
```

```{r}
boot <- function(x, n = 1e5, f = mean) {
  sd(replicate(n, f(sample(x, replace = TRUE))))
}
```

@@

doParallel::registerDoParallel(NCORES)
aucs <- foreach(i = seq_len(100), .combine = "cbind") %:%
  foreach(h2 = c(0.5, 0.8), .combine = "rbind") %dopar% {
    S <- rnorm(nsimu, mean = 0, sd = sqrt(h2))
    E <- rnorm(nsimu, mean = 0, sd = sqrt(1 - h2))
    Y <- (S + E) > qnorm(1 - K)

    bigstatsr::AUC(S, Y)
  }
doParallel::stopImplicitCluster()
apply(aucs, 1, summary)
```

@@

  y.simu <- y.simu / sd(y.simu) * sqrt(h2)
  stopifnot(all.equal(drop(var(y.simu)), h2))
  S <- y.simu
  y.simu <- S + rnorm(nrow(G), sd = sqrt(1 - h2))
  pheno <- as.numeric(y.simu > qnorm(1 - K))
  AUC(S, pheno)
}
```

@@

  # Simulate phenotypes
  AUC <- get_oracle(
    G,    
    h2 = params[["par.h2"]], 
    M = as.integer(par.causal[1]), 
    ind.possible = `if`(par.causal[2] == "all", cols_along(G), ind.HLA),
    effects.dist = params[["par.dist"]], 
    model = params[["par.model"]], 
    K = 0.3                 
  )

@@

#### On all 22 chromosomes

```{r}
doParallel::registerDoParallel(NCORES)
oracles <- foreach(i = rows_along(params.grid2), .combine = "rbind") %dopar% {
  AUC_oracle(G, params.grid2[i, ], ind.HLA)
}
doParallel::stopImplicitCluster()
```

```{r}
oracles %>% 
  mutate(
    par.causal = factor(map_chr(par.causal, ~paste(.x[1], .x[2], sep = " in ")),
                        levels = c("30 in HLA", paste(3 * 10^(1:3), "in all")))) %>%
  group_by(par.causal, par.dist, par.h2, par.model) %>%
  summarise(AUC_mean = round(mean(AUC), 4),
            AUC_mean_boot = round(boot(AUC), 4)) %>%
  print(n = Inf)
```

#### On only the chromosome 6

@@

doParallel::registerDoParallel(NCORES)
oracles_chr6 <- foreach(i = rows_along(params.grid2), .combine = "rbind") %dopar% {
  AUC_oracle(G6, params.grid2[i, ], ind.HLA6)
}
doParallel::stopImplicitCluster()
```

```{r}
tmp <- oracles_chr6 %>% 
  mutate(
    par.causal = factor(map_chr(par.causal, ~paste(.x[1], .x[2], sep = " in ")),
                        levels = c("30 in HLA", paste(3 * 10^(1:3), "in all")))) %>%
  group_by(par.causal, par.dist, par.h2, par.model) %>%
  summarise(AUC_mean = round(mean(AUC), 4),
            AUC_mean_boot = round(boot(AUC), 4)) %>%
  print(n = Inf)
```

>>>>

```{r, message=FALSE}
library(tidyverse)
library(bigsnpr)
library(doParallel)
celiac2 <- snp_attach("backingfiles/celiacQC_sub1.rds")
CHR <- celiac2$map$chromosome
POS <- celiac2$map$physical.pos
G <- celiac2$genotypes
ind.HLA <- snp_indLRLDR(CHR, POS, subset(LD.wiki34, ID == "hild12"))
```

@@

registerDoParallel(cl <- makeCluster(nb_cores()))
aucs <- foreach(i = seq_len(100), .combine = "cbind") %:%
  foreach(h2 = c(0.5, 0.8), .combine = "rbind") %dopar% {

    S <- rnorm(nsimu, mean = 0, sd = sqrt(h2))
    E <- rnorm(nsimu, mean = 0, sd = sqrt(1 - h2))
    Y <- (S + E) > qnorm(1 - K)

    bigstatsr::AUC(S, Y)
  }
stopCluster(cl)

apply(aucs, 1, summary)
```

@@

  y.simu <- y.simu / sd(y.simu) * sqrt(h2)
  stopifnot(all.equal(drop(var(y.simu)), h2))
  S <- y.simu
  y.simu <- S + rnorm(nrow(G), sd = sqrt(1 - h2))
  pheno <- as.numeric(y.simu > qnorm(1 - K))
  bigstatsr::AUC(S, pheno)
}
```

@@

  # Simulate phenotypes
  AUC <- get_oracle(
    G,    
    h2 = params[["par.h2"]], 
    M = as.integer(par.causal[1]), 
    ind.possible = `if`(par.causal[2] == "all", bigstatsr::cols_along(G), ind.HLA),
    effects.dist = params[["par.dist"]], 
    model = params[["par.model"]], 
    K = 0.3                 
  )

@@

#### With all 22 chromosomes

```{r}
registerDoParallel(cl <- makeCluster(nb_cores()))
oracles <- foreach(i = rows_along(params.grid2), .combine = "rbind") %dopar% {
  AUC_oracle(G, params.grid2[i, ], ind.HLA)
}
stopCluster(cl)
```

```{r}
boot <- pkg.paper.PRS::boot
```

```{r}
oracles %>% 
  mutate(
    par.causal = factor(map_chr(par.causal, ~paste(.x[1], .x[2], sep = " in ")),
                        levels = c("30 in HLA", paste(3 * 10^(1:3), "in all")))) %>%
  group_by_at(vars(starts_with("par"))) %>%
  summarise(AUC_mean = round(mean(AUC), 4),
            AUC_mean_boot = round(boot(AUC), 4)) %>%
  arrange(AUC_mean) %>%
  print(n = Inf)
```

#### With chromosome 6 only

@@

registerDoParallel(cl <- makeCluster(nb_cores()))
oracles_chr6 <- foreach(i = rows_along(params.grid2), .combine = "rbind") %dopar% {
  AUC_oracle(G6, params.grid2[i, ], ind.HLA6)
}
stopCluster(cl)
```

```{r}
oracles_chr6 %>% 
  mutate(
    par.causal = factor(map_chr(par.causal, ~paste(.x[1], .x[2], sep = " in ")),
                        levels = c("30 in HLA", paste(3 * 10^(1:3), "in all")))) %>%
  group_by_at(vars(starts_with("par"))) %>%
  summarise(AUC_mean = round(mean(AUC), 4),
            AUC_mean_boot = round(boot(AUC), 4)) %>%
  arrange(AUC_mean) %>%
  print(n = Inf)
```
